%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[colorlinks=true, urlcolor=blue, linkcolor=red]{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{debjit mandal} % Your name
\address{\href{https://debjit-mandal.is-a.dev}{{https://debjit-mandal.is-a.dev}}} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(+91) 8335024039 \\ debjitmandal8925@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
%--copy and paste this region  if you need more--
{\bf Kalinga Institute of Industrial Technology} \hfill {\em 2022 - 2026} 
\\ B.Tech, Computer Science and Engineering \hfill { GPA: 9.12 }
\\ 

%--copy and paste this region  if you need more--

\end{rSection}
%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}
%--copy and paste this region  if you need more--
\href{https://1drv.ms/i/s!AqmF3ryI8xyngdlvi5puoHlWRF5NTQ?e=hyfCRH}{{\bf CAMPUS AMBASSADOR}{, IMUNA}} \hfill {\em JULY, 2023- AUGUST, 2023}
\begin{itemize}
    \item Promoted IMUN Online Conferences in different schools/universities and got 10+ registrations.
    \item Best Intern for a week.
\end{itemize}
%--copy and paste this region  if you need more--
\end{rSection}
%--------------------------------------------------------------------------------
%    PROJECTS
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}
%--copy and paste this region  if you need more--
\begin{itemize}
\item{\href{https://github.com/debjit-mandal/dsh}{{\bf DSH:}}
 A Command-Line shell made using C++.
\end{itemize}
%--copy and paste this region  if you need more--
%--copy and paste this region  if you need more--
\begin{itemize}
\item{\href{https://github.com/debjit-mandal/Brain-Tumor-Detection}{{\bf Brain Tumor Detection:}}
 A project that leverages deep learning techniques to automate the detection of brain tumors from MRI images.
\end{itemize}
%--copy and paste this region  if you need more--
%--copy and paste this region  if you need more--
\begin{itemize}
\item {\href{https://github.com/debjit-mandal/NVIDIA-Stock-Analysis}
{{\bf NVIDIA Stock Analysis:}}
 A comprehensive analysis of NVIDIA Corporation's (NASDAQ: NVDA) stock performance using statistical methods and machine learning.
\end{itemize}
%--copy and paste this region  if you need more--
%--copy and paste this region  if you need more--
\begin{itemize}
\item{\href{https://github.com/debjit-mandal/cifar10-resnet-classification}{{\bf CIFAR-10 ResNet Classification:}}
 A project which focuses on classifying images from the CIFAR-10 dataset using a Residual Network (ResNet) architecture. 
\end{itemize}
%--copy and paste this region  if you need more--
%--copy and paste this region  if you need more--
\begin{itemize}
\item{\href{https://github.com/debjit-mandal/Mental-Health-Analysis}{{\bf Mental Health Analysis:}}
 A detailed analysis of a mental health dataset, utilizing various machine learning and deep learning models to classify user inputs related to mental health conditions and casual greetings.
\end{itemize}
%--copy and paste this region  if you need more--
%--copy and paste this region  if you need more--
\begin{itemize}
\item{\href{https://github.com/debjit-mandal/market-mood-analysis}{{\bf Market Mood Index(MMI) Analysis:}}
 A project that analyzes the relationship between the Market Mood Index (MMI) and the NIFTY Index from 2012 to 2024.
\end{itemize}
%--copy and paste this region  if you need more--
%--copy and paste this region  if you need more--
\begin{itemize}
\item{\href{https://github.com/TensorTrove/DriveSense}{{\bf DriveSense:}}
 An advanced smart car assistant system that combines conversational AI with video processing and machine learning capabilities.
\end{itemize}
%--copy and paste this region  if you need more--
\end{rSection}
%--------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{PROGRAMMING LANGUAGES AND TOOLS}

\\Python, scikit-learn, NumPy, pandas, TensorFlow, Excel, PowerBI, MySQL, Matplotlib, C, NLP, JavaScript, Go, Rust, MongoDB, Git, SourceHut, GitHub, GitLab\\\\
\end{rSection}
\end{document}----------------------------

