%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.6in,top=0.05in,right=0.6in,bottom=0.5in]{geometry} % Document margins
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage[colorlinks=true, urlcolor=blue, linkcolor=red]{hyperref}
\hypersetup{pdfnewwindow=true} % Open links in a new tab
\usepackage{setspace} 
\setstretch{0.55}  % Adjust line spacing (default is 1.0)

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
% \name{debjit mandal} % Your name
% \address{\href{https://debjit.is-a.dev}{{https://debjit.is-a.dev}}} % Your address
% %\address{123 Pleasant Lane \\ City, State 12345} % Your secondary address (optional)
% \address{(+91) 8335024039 \\ mystichronlicle@zohomail.in} % Your phone number and email

\begin{document}
\begin{center}
{\Huge \bf DEBJIT MANDAL}\\ % Name in full capital letters and larger size
\vspace{-2pt} % Maintain reduced vertical space between name and links
\begin{tabular}{ c c }
 \\ \faEnvelopeO\enspace mystichronlicle@zohomail.in & \faMobile\enspace (+91) 8335024039\\  
\end{tabular}
\vspace{-0.5pt} % Slight reduction in space between the two rows
\begin{tabular}{ c c c }
 \faGlobe\enspace \href{https://debjit.is-a.dev}{debjit.is-a.dev} & \faGithub\enspace \href{https://github.com/mystichronicle}{mystichronicle} & \faLinkedin\enspace \href{https://linkedin.com/in/mystichronicle}{mystichronicle}\\  
\end{tabular}
\end{center}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education} 
{\bf Kalinga Institute of Industrial Technology, Bhubaneswar, Odisha} \hfill {\em 2022 - 2026} 
\\ B.Tech, Computer Science and Engineering \hfill {CGPA: 9.13/10}

\end{rSection}\vspace{-5pt}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}
\href{}{{\bf CAMPUS AMBASSADOR}{, IMUNA}} \hfill {\em JULY, 2023 - AUGUST, 2023}\vspace{-3pt}
\begin{itemize}\setlength{\itemsep}{-6pt}
    \item Promoted IMUN Online Conferences in different schools/universities and got 10+ registrations.
    \item Best Intern for a week.
\end{itemize}
\end{rSection}\vspace{-5pt}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Projects}
\begin{itemize}\setlength{\itemsep}{-0.5pt}
    \item{\href{https://github.com/mystichronicle/NeuroSeg}{{\bf NeuroSeg:}} 
    A Deep Learning-based Brain Tumor Segmentation System.\vspace{-2pt} 
    \begin{itemize}\setlength{\itemsep}{-6pt}
        \item Designed and trained a UNet-based deep learning model for automatic brain tumor segmentation from MRI images.
        \item Developed a full-stack web application using Flask (backend) and HTML/CSS/JS (frontend) for real-time tumor detection.
    \end{itemize}}
    
    \item{\href{https://github.com/mystichronicle/ECGShield}{{\bf ECGShield:}} 
    An interactive Streamlit-based system for ECG noise removal using advanced filtering techniques.\vspace{-2pt} 
    \begin{itemize}\setlength{\itemsep}{-6pt}
        \item Implemented various signal filtering techniques including Notch Filter, High-Pass, Low-Pass, and Wavelet Denoising.
        \item Designed a user-friendly Streamlit interface to upload ECG files, visualize signals, and download the cleaned output.
    \end{itemize}}

    \item{\href{https://github.com/mystichronicle/MoodMelody}{{\bf MoodMelody:}} 
    A Real-time emotion detection and content recommendation system.\vspace{-2pt} 
    \begin{itemize}\setlength{\itemsep}{-6pt}
        \item Implemented emotion recognition using TensorFlow/Keras.
        \item Integrated Spotify API for personalized music recommendations.
    \end{itemize}}
    
    \item{\href{https://github.com/mystichronicle/dsh}{{\bf DSH:}}
    A Command-Line shell made using C++.\vspace{-2pt} 
    \begin{itemize}\setlength{\itemsep}{-6pt}
        \item Implemented custom command parsing for user-defined commands.
        \item Handled concurrency with multithreading for running background processes.
    \end{itemize}}
    
    \item{\href{https://github.com/mystichronicle/TrafficVisionAI}{{\bf TrafficVisionAI:}} 
    A Real-Time Traffic Sign Recognition and Driver Assistance using AI.\vspace{-2pt} 
    \begin{itemize}\setlength{\itemsep}{-6pt}
        \item Integrated traffic sign recognition using TensorFlow and OpenCV.
        \item Developed lane detection and collision warning systems.
    \end{itemize}}
    
\end{itemize}
\end{rSection}\vspace{-5pt}

%----------------------------------------------------------------------------------------
%	PATENTS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Patents}
\begin{itemize}\setlength{\itemsep}{-4pt}
    \item {\href{https://mystichronicle.github.io/patent-uk-1/}{\bf UK Design Patent -- Autonomous Vehicle Predictive Steering Device} \hfill {\em Design No. 6424920}\vspace{-2pt} 
    \begin{itemize}\setlength{\itemsep}{-6pt}
    \item Registered on 20 February 2025; Granted on 07 March 2025. Co-held with MR. PRITAM\\  
     CHAKRABORTY, MR. NILOTPAL BASU, and DR. ANJAN BANDYOPADHYAY.
    \item Developed an innovative steering mechanism that enhances predictive capabilities in autonomous vehicles.
    \end{itemize}}
    
\end{itemize}
\end{rSection}\vspace{-5pt}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}
\begin{itemize}\setlength{\itemsep}{-6pt}
    \item {\bf Programming Languages:} Python, C/C++
    \item {\bf Web Technologies:} HTML, CSS
    \item {\bf Tools:} Git
    \item {\bf Frameworks \& Libraries:} TensorFlow, OpenCV, scikit-learn, Pandas, NumPy
    \item {\bf Databases:} SQLPlus
\end{itemize}
\end{rSection}\vspace{-5pt}
\end{document}----------------------------

